Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-13 main.tex
Details how with-me-ness is computed -- Pierre's suggestion

We also conducted a quantitative assessment of the engagement levels of the
children. Table~\ref{tab:results-with-me-ness} reports the levels of
\emph{with-me-ness} of the children during the second study at school A.
\emph{With-me-ness} is a quantifiable precursor of engagement: it measures the
percentage of time spent by the child focusing on the task at hand. This metric
was first devised in the context of computer-supported
learning~\cite{sharma2014me}, and we have previously studied its applicability
to human-robot interaction and formalized the exact methodology
in~\cite{lemaignan2016realtime}\footnote{Note that with-me-ness is a metric that
allows real-time computation by the robot itself: while we did not yet make
use of it, it does in principle allow the robot to detect on-line possible
disengagements, and eventually address them by adapting its physical
behavior, switching to different activities, etc.}.

>>>>

We also conducted a quantitative assessment of the engagement levels of the
children. Table~\ref{tab:results-with-me-ness} reports the levels of
\emph{with-me-ness} of the children during the second study at school A.
\emph{With-me-ness} is a quantifiable precursor of engagement: it measures the
percentage of time spent by the child focusing on the task at hand. This metric
was first devised in the context of computer-supported
learning~\cite{sharma2014me}, and we have previously studied its applicability
to human-robot interaction and formalized the exact methodology
in~\cite{lemaignan2016realtime}. We compute it by first estimating the focus of
attention of the child over the course of the interaction (using real-time 6D
head pose estimation); then, by matching this measured focus of attention
with the \emph{expected} attentional targets. For instance, when the child is supposed
to write a demonstration, we expect him to look at the tablet if he is actually
engaged into the task; when the robot is telling a story,
we expect the engaged child to look at the robot, etc. The resulting values
(Table~\ref{tab:results-with-me-ness}) represent therefore the percentage of
interaction where each of the children were actually focusing on the task\footnote{Note that
with-me-ness is a metric that allows real-time computation by the robot
itself: while we did not yet make use of it, it does in principle allow the
robot to detect on-line possible disengagements, and eventually address them
by adapting its physical behavior, switching to different activities, etc.}.
